\name: Deterministic and Coherent Implicits

### 2017-02-16 src/Translation.tex

The gray extension to the syntax of type environments annotates very
implicit rule type with explicit System F evidence in the form of a 
term variable $x$.

@@

For simple types rule $\type$ rule \mylabel{R-Simp} delegates the work of
building evidence, when a matching rule $\rulet$ type is found in the
environment, to rule \mylabel{L-RuleMatch}. The evidence consists of two parts:
$E$ is the evidence of matching $\type$ against $\rulet$. This match contains
placeholders $\bar{x}$ for the contexts whose resolution is postponed by rule
\mylabel{M-IAbs}. It falls to rule \mylabel{L-RuleMatch} to perform these
postponed resolutions, obtain their evidence $\bar{E}$ and fill in the
placeholders.

@@

With the evidence we can state the correctness of the algorithm.
\begin{theorem}[Partial Correctness]
Let $\tenv$ be a type environment, $\rulet$ be a type and E be a System F expressions.
Assume that $\epsilon \vdash_{\mathit{unamb}} \rulet$ and also $\forall \rulet_i \in \tenv: \epsilon \vdash_{\mathit{unamb}} \rulet_i$.
Then $\tenv \ivturns \rulet \leadsto E$ if and only if $\tenv \vdash_{\mathit{alg}} \rulet \leadsto E$,
provided that the algorithm terminates.
\end{theorem}

>>>>

The gray extension to the syntax of type environments annotates every
implicit rule type with explicit System F evidence in the form of a 
term variable $x$.

@@

For simple types $\type$ rule \mylabel{R-Simp} delegates the work of
building evidence, when a matching rule $\rulet$ type is found in the
environment, to rule \mylabel{L-RuleMatch}. The evidence consists of two parts:
$E$ is the evidence of matching $\type$ against $\rulet$. This match contains
placeholders $\bar{x}$ for the contexts whose resolution is postponed by rule
\mylabel{M-IAbs}. It falls to rule \mylabel{L-RuleMatch} to perform these
postponed resolutions, obtain their evidence $\bar{E}$ and fill in the
placeholders.

@@

With the evidence we can state the correctness of the algorithm.
\begin{theorem}[Partial Correctness]
Let $\tenv$ be a type environment, $\rulet$ be a type and E be a System F expression.
Assume that $\epsilon \vdash_{\mathit{unamb}} \rulet$ and also $\forall \rulet_i \in \tenv: \epsilon \vdash_{\mathit{unamb}} \rulet_i$.
Then $\tenv \ivturns \rulet \leadsto E$ if and only if $\tenv \vdash_{\mathit{alg}} \rulet \leadsto E$,
provided that the algorithm terminates.
\end{theorem}
